Coexistence with varying environmental filtering intensity

### 2018-07-02 env_intensity.Rmd
:sparkles: Simulate traits with arbitrary number of species

### Moderately correlated traits
```{r}
generate_cor_traits = function(number_patches, number_other = 9, cor_coef = 0.7) {

    # Initial Trait
    x1 = seq(1, number_patches)

@@

        # Independent trait
        x2 = runif(number_patches, 1, number_patches)

@@

devtools::load_all()
# Initial parameters -----------------------------------------------------------
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 50   # initial population size
n_traits <- 4    # number of traits
k        <- 1.45 # Niche height
width    <- seq(10, 10, length.out = patches) # Niche breadth

@@

# Generate traits --------------------------------------------------------------
set.seed(1)
traits <- generate_cor_traits(patches, n_traits - 1, cor_coef = 0.3)
colnames(traits) <- paste0("trait", seq(n_traits))
rownames(traits) <- paste0("species", seq(species))

>>>>

### Moderately correlated traits
```{r}
generate_cor_traits = function(number_patches, number_species, number_other = 9,
                               cor_coef = 0.7) {

    # Initial Trait
    x1 = seq(1, number_patches, length.out = number_species)

@@

        # Independent trait
        x2 = runif(number_species, 1, number_patches)

@@

devtools::load_all()
# Initial parameters -----------------------------------------------------------
patches  <- 25   # Number of patches
species  <- 1000   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 50   # initial population size
n_traits <- 4    # number of traits
k        <- 1.45 # Niche height
width    <- seq(10, 10, length.out = patches) # Niche breadth

@@

# Generate traits --------------------------------------------------------------
set.seed(1)
traits <- generate_cor_traits(patches, species, n_traits - 1, cor_coef = 0.3)
colnames(traits) <- paste0("trait", seq(n_traits))
rownames(traits) <- paste0("species", seq(species))
